\cvsec{EXPRERIENCE}

\begin{cventries}
  \cventry
    {Wix.com}
    {Software Developer}
    {Beersheba/Tel Aviv, Israel}
    {February 2017 - November 2019}
    {
      \begin{cvitems}
        \item {My first project involved refactoring the Wix Contacts app. My focus was mainly on front-end components and architecture. Technology wise, we were moving away from angular 1.x to a \mylib{React/Mobx} combo on the front-end, with a \mylib{node.js/scala} back-end solution. }
        \item {Technical lead in Wix Forms, tasked with creating the first app to run compleltely on Editor's new platform.\\ 
        I focused primarily on designing the underlying messaging architecture, which involved delving deep into \mylib{Web Worker} mechanics and implementing event-based communication protocols between disparate app components.}
        \item {I contributed code to Wix Editor, where my largest contribution was extracting, redesigning and externalising the monolithic user authentication mechanism underlying all editor-based sites. It was one of the more challenging projects I have worked on. Consequently, it is also one of my proudest accomplishments.}
        \item {My last position was technical team lead in Wix Bookings. I've introduced a new technology (\mylib{React Hooks}) into the teams' legacy codebase. This also set the stage and tooling for future refactoring projects across Bookings.}
      \end{cvitems}
     }

    \begin{cvskills}
      \cvskill {Languages} {\mylib{JavaScript}, \mylib{TypeScript}}
      \cvskill {Technologies} {\mylib{React}, \mylib{Redux/Mobx}, \mylib{Node.js}, \mylib{TeamCity/TravisCI}, \mylib{Git(Hub)}}
    \end{cvskills}

  \cventry
    {Esti Yeger-Lotem Lab, National Institute of Biotechnology in the Negev}
    {Software Developer}
    {Beersheba, Israel}
    {February 2014 - February 2017}
    {
      \begin{cvitems}
        \item {Developing interactive single-page web applications for visualizing complex protein-interaction networks.}
        \item {Developing light, RESTful API interfaces in Python (utilizing \mylib{flask}, and \mylib{Celery} for async computation tasks ).}
        \item {Created a utility library for manipulating large graph data-structures using a functional approach.}
        \item {Refactoring several legacy JavaScript apps, leveraging current frameworks (Backbone) to simplify codebase.}
        \item {Introducing new JavaScript visualization libraries and creating reusable scaffolding for graph components.}
        \item {Administering server infrastructure and backup.}
      \end{cvitems}
    }
    
    \begin{cvskills}
      \cvskill {Languages} {\mylib{JavaScript}, \mylib{Python}}
      \cvskill {Technologies} {\mylib{Backbone/React}, \mylib{D3.js}, \mylib{Cytoscape.js} \mylib{Flask}, \mylib{MySQL}, \mylib{Apache}}
    \end{cvskills}
    
  \cventry
    {Solbar Industries}
    {Systems Administrator}
    {Ashdod, Israel}
    {July 2010 - October 2013}
    {
      \begin{cvitems}
        \item {IT administrator of 4 international branches.}
      \end{cvitems}
    }
    \vspace{3.0mm}

  \cventry
    {Israel Defense Forces}
    {Network Administrator}
    {Tel HaShomer, Israel}
    {December 2007 - July 2010}
    {}
    \vspace{-5.0mm}

\end{cventries}

